\section{Experience}
\resumeSubheading
  {Optimizely Inc.}{Dhaka, Bangladesh}
  {Software Engineer II}{Sep 2023 - Present}
  \resumeItemListStart
    \resumeItem{Working in the Rapid Experimentation Services team for the leading DXP provider to facilitate integration with external CMS, DAM, and CMP systems.}
    \resumeItem{Migrated a large volume of data (in TBs) using custom migration modules \textit{(Python, S3, Redshift)} by leveraging different microservice APIs.}
    \resumeItem{Streamlined 6+ client data analysis reports \textit{(Python, Jenkins)} via automated data pipelines.}
    \resumeItem{Developed data extraction and migration pipelines \textit{(Flask, Python, AWS)} for multiple CMS and DAM services such as Kapost, Bynder, ImageVault, Widen, and more.}
\resumeItemListEnd
\vspace{7pt}
\resumeSubheading
  {Intelligent Machines Ltd}{Dhaka, Bangladesh}
  {Software Engineer}{Mar 2021 - Aug 2023}
  \resumeItemListStart
    \resumeItem{Designed overall service architecture and pipelines for 3 projects \textit{(MongoDB, Express, ReactJs, NodeJs)}. Also, handled the deployment of the microservice-based backends \textit{(Docker, Kubernetes)}.}
    \resumeItem{Engineered a highly scalable middleware solution \textit{(NodeJs, Express, ScyllaDB, Redis)} facilitating seamless transactions between two payment systems, ensuring a high throughput.}
    \resumeItem{Implemented data pipeline across multiple AI and Analytics servers using message brokers  \textit{(RabbitMQ)} as a core service, boosting data transfer by 40\%.}
    \resumeItem{Built fully automated CI/CD pipelines for containerized Node applications \textit{(Docker, Azure CR)}.}
    \resumeItem{Developed backends for multiple projects \textit{(Express, Django)} ensuring data security and best principles.}
    \resumeItem{Worked in the development of multiple responsive web applications \textit{(ReactJs, NextJs)}.}
\resumeItemListEnd
\vspace{7pt}
\resumeSubheading
  {Field Information Solutions GmbH/Ltd}{Dhaka, Bangladesh}
  {Junior Software Engineer $\rightarrow$ Software Engineer}{Jul 2019 - Mar 2021}
  \resumeItemListStart
    \resumeItem {Led the development of Microfinance mobile Android app maintaining security principles, optimizing memory \& database queries, and implementing 4 complex core modules \textit{(Java, Android SDK, MongoDB Realm)} to digitize and analyze credit procedures.}
    \resumeItem {Improved the efficiency of an on-demand intelligent offline sync engine up to 25\% \textit{(Java, Android SDK)} to enable data synchronization in unreliable internet on lower-end Android devices.}
    \resumeItem{Reduced memory leaks by 95\% \textit{(Android Debug Tools)} by optimizing legacy codes and resource usage.}
    \resumeItem {Developed features for internal libraries and implemented deployment pipelines \textit{(Java, Jenkins)} for the flagship SaaS product modules that include Geo-mapping, Inventory Manager, Dynamic Surveys, and Report Engine.}
    \resumeItem{Mentored 2 junior engineers and received exceptional feedback on teamwork and leadership.}
    \resumeItemListEnd

